### 2023-06-10 source/analysis/exploration/ExploreOutcomes.Rmd
#23 HUGE RESTRUCTURE

plot_grid(wage_plot, wratio_plot, const_plot, align="v", axis="b", ncols=1)
ggsave("const_wages.png", device = "png", path="analysis/output/exploration")
```

>>>>

plot_grid(wage_plot, wratio_plot, const_plot, align="v", axis="b", ncols=1)
# ggsave("const_wages.png", device = "png", path="analysis/output/exploration")
```
